DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-07 child_single_geo.Rmd
handles different crs

```{r} 
#library(broom)

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

>>>>

```{r}

this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
if (!is.na(st_crs(ncdf)$epsg) & !is.na(st_crs(this_geo)$epsg) & 
    st_crs(ncdf)$epsg != st_crs(this_geo)$epsg) {
  ncdf <- st_transform(ncdf, st_crs(this_geo)$epsg)
  nc_sw_sh <- st_transform(ncdf, st_crs(this_geo)$epsg)
}
this_roads <- st_intersection(ncdf, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))
